paper_replication

### 2021-12-15 paper_replication.Rmd
Update paper_replication.Rmd

# Model Summaries (Note coefficients are per 1000 women)
table_3 <- tibble(Characteristic = "Highly Restrictive Legislation",
                  Beta = model_no_dist$coefficients[2]*1000,
                  "p-value" = c('< 0.001')) %>% 
  kbl(caption = "Table 3: Change in Abortions per 1000 Women in Model without Distances", 
          digits = 3)

>>>>

# Model Summaries (Note coefficients are per 1000 women)
table_3 <- tibble(Characteristic = "Highly Restrictive Legislation",
                  Beta = model_no_dist$coefficients[2]*1000,
                  "p-value" = c('< 0.001')) %>% 
  kbl(caption = "Table 3: Change in Abortions per 1000 Women in Model without Distances", 
          digits = 3)
print(table_3)
